Network Configuration Synthesis with Abstract Topologies \vspace{1cm}

### 2017-03-14 paper/abstraction/paper.tex
adjust author info for more space

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{xcolor}
\usepackage{url}
\usepackage{times}
\usepackage{xspace}
\usepackage{listings}
\usepackage{code}
\usepackage{tikz}
\usetikzlibrary{arrows,automata,positioning}
\let\proof\relax
\let\endproof\relax
\usepackage{amsthm}
\usepackage{subcaption}
\usepackage{balance}
\usepackage{textcomp}
\usepackage{enumitem}
\usepackage{pifont}
\newcommand{\cmark}{\ding{51}}
\newcommand{\xmark}{\ding{55}}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}

@@

\authorinfo{Ryan Beckett}{Princeton University}{rbeckett@cs.princeton.edu}
\authorinfo{Ratul Mahajan}{Microsoft Research}{ratul@microsoft.com}
\authorinfo{Todd Millstein\thanks{Supported in part by National Science Foundation award
CNS-1161595.}}{UCLA}{todd@cs.ucla.edu}
\authorinfo{Jitendra Padhye}{Microsoft Research}{jpadhye@microsoft.com} 
\authorinfo{David Walker}{Princeton University}{dpw@cs.princeton.edu}

@@

>>>>

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{xcolor}
\usepackage{url}
\usepackage{times}
\usepackage{xspace}
\usepackage{listings}
\usepackage{code}
\usepackage{tikz}
\usetikzlibrary{arrows,automata,positioning}
\let\proof\relax
\let\endproof\relax
\usepackage{amsthm}
\usepackage{subcaption}
\usepackage{balance}
\usepackage{textcomp}
\usepackage{enumitem}
\usepackage{pifont}
\newcommand{\cmark}{\ding{51}}
\newcommand{\xmark}{\ding{55}}

@@

%\authorinfo{Ryan Beckett}{Princeton University}{rbeckett@cs.princeton.edu}
%\authorinfo{Ratul Mahajan}{Microsoft Research}{ratul@microsoft.com}
%\authorinfo{Todd Millstein}{UCLA}{todd@cs.ucla.edu}
%\authorinfo{Jitendra Padhye}{Microsoft Research}{jpadhye@microsoft.com} 
%\authorinfo{David Walker}{Princeton University}{dpw@cs.princeton.edu}

%\numberofauthors{1}

\authorinfo{Ryan Beckett$^*$\and Ratul Mahajan$^\dagger$\and Todd Millstein$^\S$\and Jitendra Padhye$^\dagger$\and David Walker$^*$}
{Princeton University$^*$, Microsoft Research$^\dagger$, University of California Los Angeles$^\S$}
{\{rbeckett,dpw\}@cs.princeton.edu, \{ratul,padhye\}@microsoft.com, todd@cs.ucla.edu}

@@

\para{Acknowledgments}
We thank the PLDI reviewers for comments on the paper. This work is supported in part by the National Science Foundation award CNS-1161595 as well as Cisco award 677002.
